Water, High-Altitude Condensates, and Methane Depletion in the Atmosphere of the Warm Neptune WASP-107\lowercase{b}

### 2017-08-18 ms.tex
edits

%Figures and Tables:
% 1.  transit light curves
% 2.  best fit spectrum
% 3.  retrieval results
% 4.  table of transit depths
% 5.  JWST predictions for cloud models

@@

We explored a few retrieval scenarios with additional complexity, including the addition of cloud patchiness \citep{line16}, a quench pressure for nitrogen and carbon species \citep[e.g.][]{morley17}, and a power law haze opacity.  These models did not significantly improve the fit quality, and the main retrieval results were unchanged.  We also explored cases without the $30\times$ solar metallicity prior upper limit. Without this prior, metallicities up to $100\times$ were permitted, but other parameters were not significantly changed. 
%We also tested the effect of varying the planet's surface gravity within the published FIXME $\sigma$ range, and found that our results were again minimally changed.

@@

We also performed a ``free" retrieval that allowed the abundances of CH$_4$, H$_2$O and NH$_3$ to vary with no assumption of chemical equilibrium. The retrieved methane abundance is low ($3\times10^{-11} - 3\times10^{-6}$ at 68\% confidence). We rule out at $3\,\sigma$ confidence the predicted methane abundance for a composition with solar C/O and $3\,\times$ solar metallicity (the median metallicity from the chemical equilibrium retrieval).  Based on these tests, we conclude that the atmosphere of WASP-107b is depleted in methane relative to expectations for a solar abundance pattern. By contrast, the water abundance ($6\times10^{-6} - 2\times10^{-3}$) is consistent with predictions (FIXME).

@@

These photochemical hazes are assumed to form from hydrocarbons generated by methane photolysis; however, we found in the previous section that methane is depleted.  Furthermore, even if the precursors were present, it is unclear whether the 100\% haze production efficiency is realistic.  However, organic hydrocarbons are not the only possible photolytic haze in cool H2-rich atmospheres. Sulfur chemistry may create additional haze material \citep{zahnle09, gao17}. Further modeling and laboratory work of the hazes that form in these conditions is needed for a satisfactory explanation of the data.

>>>>

@@

We explored a few retrieval scenarios with additional complexity, including the addition of cloud patchiness \citep{line16}, a quench pressure for nitrogen and carbon species \citep[e.g.][]{morley17}, and a power law haze opacity.  We also varied the assumed planet mass by $3\,sigma$. These models did not significantly improve the fit quality, and the main retrieval results were unchanged.  We also explored cases without the $30\times$ solar metallicity prior upper limit. Without this prior, metallicities up to $100\times$ were permitted, but other parameters were not significantly changed. 
%We also tested the effect of varying the planet's surface gravity within the published FIXME $\sigma$ range, and found that our results were again minimally changed.

@@

We also performed a ``free" retrieval that allowed the abundances of CH$_4$, H$_2$O and NH$_3$ to vary with no assumption of chemical equilibrium. The $3\,\sigma$ upper limit on methane abundance is $1.2\times10^{-3}$, ruling out the the predicted methane content for a composition with solar C/O and $3\,\times$ solar metallicity (the median metallicity from the chemical equilibrium retrieval).  Based on these tests, we conclude that the atmosphere of WASP-107b is depleted in methane relative to expectations for a solar abundance pattern. By contrast, the water abundance ($6\times10^{-6} - 2\times10^{-3}$) is consistent with predictions for solar composition.

@@

These photochemical hazes are assumed to form from hydrocarbons generated by methane photolysis; however, we found in the previous section that methane is depleted.  Furthermore, even if the precursors were present, it is unclear whether the 100\% haze production efficiency is realistic.  However, organic hydrocarbons are not the only possible photolytic haze in cool H2-rich atmospheres, as sulfur chemistry may create additional haze material \citep{zahnle09, gao17}. Further modeling and laboratory work of the hazes that form in these conditions is needed for a satisfactory explanation of the data.
